Dynamics of isoflurane-induced vasodilation and blood flow of cerebral vasculature revealed by multi-exposure speckle imaging

### 2021-08-18 article.tex
Updates for journal requirements
- Include ARRIVE guidelines
- Declaration of Interest
- CRediT Statement

Mice were housed 1-4 per cage in a conventional vivarium maintained at 20 $^\circ$C on 12-hour light-to-dark cycles (07:00 to 19:00). All subjects received standard cage supplements (e.g. cage enclosures, nesting material, and wooden toys) with water and food \textit{ad libitum}. All animal protocols were designed in accordance with the National Institutes of Health Guide for the Care and Use of Laboratory Animals and were approved by the Institutional Animal Care and Use Committee at The University of Texas at Austin.

@@

\section*{Disclosures}
A.K.D. holds equity in Dynamic Light, Inc. The authors declare no other conflicts of interest.

\section*{Author Contributions}
C.T.S. and L.M.R. constructed the imaging system, conceived the experiments, and acquired the data. C.T.S analyzed the results and wrote the manuscript. F.H. performed the animal surgeries. L.L. and A.K.D. supervised the project. All authors contributed to the manuscript revisions.

>>>>

Mice were housed 1-4 per cage in a conventional vivarium maintained at 20 $^\circ$C on 12-hour light-to-dark cycles (07:00 to 19:00). All subjects received standard cage supplements (e.g. cage enclosures, nesting material, and wooden toys) with water and food \textit{ad libitum}. All animal protocols were designed in accordance with the National Institutes of Health Guide for the Care and Use of Laboratory Animals in compliance with ARRIVE guidelines and were approved by the Institutional Animal Care and Use Committee at The University of Texas at Austin.

@@

\section*{Declaration of Interest}
A.K.D. holds equity in Dynamic Light, Inc. The authors declare no other conflicts of interest.

\section*{CRediT Statement}
\textbf{Colin T. Sullender:} Conceptualization, Methodology, Software, Validation, Investigation, Data Curation, Formal Analysis, Writing - Original Draft, and Visualization. \textbf{Lisa M. Richards:} Conceptualization, Methodology, Investigation, Data Curation, Writing - Review \& Editing. \textbf{Fei He:} Investigation, Resources, Writing - Review \& Editing. \textbf{Lan Luan:} Writing - Review \& Editing, Supervision, and Funding Acquisition. \textbf{Andrew K. Dunn:} Conceptualization, Writing - Review \& Editing, Supervision, Funding Acquisition, and Project Administration.
